### 2015-03-13 ResearchNotes/Notes.Rmd
A few more modifications to the model.  I may do more with the shell but this is close to done.

summary(lm(KWH~TOTSQFT_EN:HDD65+TOTSQFT_EN:CDD65 +Householder_Race+KOWNRENT:TYPEHUQ 
           + ElecMeals
           + NUMFRIG+AgeFridge
           + TVONWD1:TVTYPE1
           + NUMPC+TIMEON1
           + WELLPUMP
           + ElecWater
           + SWIMPOOL + ElecPool
           + RECBATH +ElecTub
           + TYPEGLASS, data=RECS[RECS$KOWNRENT!="Free" & RECS$NWEIGHT<40000 & RECS$NUMFRIG<5,]))
```

@@

summary(lm(KWH~TOTSQFT_EN:HDD65+TOTSQFT_EN:CDD65 +Householder_Race+KOWNRENT:TYPEHUQ 
           + ElecMeals
           + NUMFRIG+AgeFridge
           + TVONWD1:TVTYPE1
           + NUMPC+TIMEON1
           + WELLPUMP
           + ElecWater
           + SWIMPOOL + ElecPool
           + RECBATH +ElecTub
           + TYPEGLASS
           + NHSLDMEM, data=RECS[RECS$KOWNRENT!="Free" & RECS$NWEIGHT<40000 & RECS$NUMFRIG<5,]))
```

Need to add income and all the heating and cooling things, ethnicity and structure type/ own rent.

Time to see if the behaviors are different, all exogenous.  Checking temperatures

>>>>

summary(lm(KWH~TOTSQFT_EN:HDD65+TOTSQFT_EN:CDD65 +Householder_Race+KOWNRENT:TYPEHUQ 
           + ElecMeals
           + NUMFRIG+AgeFridge
           + TVONWD1:TVTYPE1
           + NUMPC+TIMEON1
           + WELLPUMP
           + ElecWater
           + SWIMPOOL + ElecPool
           + RECBATH +ElecTub
           + TYPEGLASS:TOTSQFT_EN, data=RECS[RECS$KOWNRENT!="Free" & RECS$NWEIGHT<40000 & RECS$NUMFRIG<5,]))
```

@@

summary(lm(KWH~TOTSQFT_EN:HDD65+TOTSQFT_EN:CDD65 +Householder_Race+KOWNRENT:TYPEHUQ 
           + ElecMeals
           + NUMFRIG+AgeFridge
           + TVONWD1:TVTYPE1
           + NUMPC+TIMEON1
           + WELLPUMP
           + ElecWater
           + SWIMPOOL + ElecPool
           + RECBATH +ElecTub
           + TYPEGLASS:TOTSQFT_EN
           + NHSLDMEM, data=RECS[RECS$KOWNRENT!="Free" & RECS$NWEIGHT<40000 & RECS$NUMFRIG<5,]))
```

Time for income.  Need to convert this to a real value from the categories and blending this in with the race and ethnicity.

summary(RECS$MONEYPY)
library(plyr)
IncomeTopCode<-150000

RECS$Income<-as.numeric(as.character(revalue(RECS$MONEYPY,c("Less2500"=1250, "Less5K"=3750, "Less7500"=6250,"Less10K"=8750,"Less15K"=12500,"Less20K"=17500,"Less25K"=22500,"Less30K"=27500, "Less35K"=32500,"Less40K"=37500,"Less45K"=42500,"Less50K"=47500,"Less55K"=52500,"Less60"=57500,"Less65"=62500,"Less70"=67500,"Less75"=72500,"Less80"=77500, "Less85"=82500, "Less90"=87500,"Less95"=92500,"Less100K"=97500,"Less120K"=110000,"Gr120K"=IncomeTopCode))))

#Setting left out to wt non-hispanic
RECS$Householder_Race<-relevel(RECS$Householder_Race,"Wt")

summary(lm(KWH~TOTSQFT_EN:HDD65+TOTSQFT_EN:CDD65 +KOWNRENT:TYPEHUQ 
           + ElecMeals
           + NUMFRIG+AgeFridge
           + TVONWD1:TVTYPE1
           + NUMPC+TIMEON1
           + WELLPUMP
           + ElecWater
           + SWIMPOOL + ElecPool
           + RECBATH +ElecTub
           + TYPEGLASS:TOTSQFT_EN
           + NHSLDMEM
           + Income:Hispanic+Householder_Race:Hispanic:Income, data=RECS[RECS$KOWNRENT!="Free" & RECS$NWEIGHT<40000 & RECS$NUMFRIG<5,]))

Now time to add structure type.  I added it just to the weather driven.

summary(lm(KWH~TYPEHUQ:KOWNRENT:TOTSQFT_EN:HDD65+TYPEHUQ:KOWNRENT:TOTSQFT_EN:CDD65 +KOWNRENT:TYPEHUQ 
           + ElecMeals
           + NUMFRIG+AgeFridge
           + TVONWD1:TVTYPE1
           + NUMPC+TIMEON1
           + WELLPUMP
           + ElecWater
           + SWIMPOOL + ElecPool
           + RECBATH +ElecTub
           + TYPEGLASS:TOTSQFT_EN
           + NHSLDMEM
           + Income:Hispanic+Householder_Race:Hispanic:Income, data=RECS[RECS$KOWNRENT!="Free" & RECS$NWEIGHT<40000 & RECS$NUMFRIG<5,]))

# Checking on behaviors
Time to see if the behaviors are different, all exogenous.  Checking temperatures
